\documentclass{resume}

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Muaaz Shoaib}
\address{+923170936845 \\ Lahore, Pakistan} 
\address{\href{mailto:muaazshoaib1670@gmail.com}{muaazshoaib1670@gmail.com} \\ \href{https://www.linkedin.com/in/muaazshoaib}{linkedin.com/in/muaazshoaib} \\ \href{https://github.com/muaazshoaib}{https://github.com/muaazshoaib}}  %

\begin{document}



\begin{rSection}{CAREER OBJECTIVE}

{I am a Flutter Developer with over one year of experience in building scalable, high-quality mobile applications using Flutter, Dart, and clean architecture principles. I am passionate about creating intuitive user experiences through innovative UI design, efficient API integrations, and performance optimization. My goal is to continue growing as a developer while contributing to impactful, real-world projects that deliver meaningful value.}

\end{rSection}



\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Dart, Flutter, GetX, RESTful API, Firebase, Clean Architecture\\
Tools & Git, GitHub, Android Studio, Visual Studio Code, Postman, Figma\\
\end{tabular}\\

\end{rSection}



\begin{rSection}{EXPERIENCE}

\textbf{Flutter Developer (Full-time)} \hfill Dec 2024 - Present\\
\textbf{\href{https://www.linkedin.com/company/codingbeats}{Coding Beats}} \hfill \textit{Lahore, Pakistan}
 \begin{itemize}
    \itemsep -5pt {} 
\item Independently built and maintained features in production-level Flutter apps, resulting in improved performance, scalability, and user satisfaction.
\item Led the development of responsive UI components and seamless API integrations for key projects, including LocumKit (Payroll System) and WePullUp (eCommerce Platform).
\item Applied Clean Architecture principles and utilized tools such as Firebase, Git, and Postman to streamline development workflows and enhance code maintainability.
\item Collaborated closely with backend developers to integrate RESTful APIs, significantly improving application functionality, responsiveness, and user experience.
\item Gained hands-on experience in Flutter development, with a strong focus on UI/UX design, state management (GetX), and efficient API consumption, contributing to project success and timely delivery.
 \end{itemize}

\textbf{Flutter Developer (Final Year Project)} \hfill Mar 2023 - May 2024\\
\textbf{\href{https://www.linkedin.com/company/comsats-university-islamabad-attock-campus/}{Comsats University Islamabad, Attock Campus}} \hfill \textit{Attock, Pakistan}
 \begin{itemize}
    \itemsep -5pt {} 
\item Developed a comprehensive productivity app using Flutter, Dart, GetX, Firebase, Git, and GitHub.
\item Boosted task completion rates by implementing categorized and prioritized task management with a dynamic calendar and reminders.
\item Improved user focus and habit-building through features like focus mode, Pomodoro timer, habit tracker, and an analytics dashboard.
 \end{itemize}

\end{rSection} 



\begin{rSection}{PROJECTS}

\textbf{WePullUp: eCommerce Platform} \hfill {}
\begin{itemize}
\item Contributed to the development of a large-scale eCommerce platform, focusing on UI components and user experience.
\item Implemented API integrations to manage multiple stores, products, courier flow, and customer data, ensuring smooth transaction processes.
\item Optimized app performance and scalability to handle high traffic and large volumes of data efficiently.
\end{itemize}

\textbf{LocumKit: Payroll Management System} \hfill {}
\begin{itemize}
\item Developed a payroll management system to streamline payment processing for professionals.
\item Integrated RESTful APIs with GetX for state management, ensuring real-time data synchronization and efficient UI performance.
\item Applied clean architecture principles to ensure scalability, maintainability, and ease of future updates.
\end{itemize}

\textbf{Productivity App (Final Year Project)} \hfill {}
\begin{itemize}
\item Developed a comprehensive productivity app using Flutter, Dart, GetX, Firebase, Git, and GitHub.
\item Boosted task completion rates by implementing categorized and prioritized task management with a dynamic calendar and reminders.
\item Improved user focus and habit-building through features like focus mode, Pomodoro timer, habit tracker, and an analytics dashboard.
\end{itemize}

\textbf{Intensify Surveillance System} \hfill {}
\begin{itemize}
\item Built a real-time surveillance app in Flutter integrating YOLO v2, MobileNet, and SSD for object detection.
\item Enabled live object recognition, tracking, and instant alerts for security use.
\item Designed intuitive UI with Flutter and applied deep learning models for accurate real-time monitoring.
\end{itemize}

\textbf{WhatsApp Clone} \hfill {}
\begin{itemize}
\item Built a full-stack messaging application using Flutter, Dart, Firebase, Agora SDK, Git, and GitHub, increasing user engagement.
\item Enhanced security and reliability by reducing login issues through secure phone number authentication.
\item Achieved an increase in user retention by implementing video calling, status updates, and Clean Architecture for maintainability.
\end{itemize}

\textbf{Flutter Chat App} \hfill {}
\begin{itemize}
\item Created a chat application with Flutter, Dart, Firebase, Firebase Cloud Messaging, Firebase Cloud Storage, Git, and GitHub, optimizing message delivery speed.
\item Improved user login success rate using seamless Firebase Authentication integration.
\item Enhanced user experience with Firebase Cloud Storage for efficient media management and push notifications for user activities.
\end{itemize}

\textbf{Bitcoin Ticker} \hfill {}
\begin{itemize}
\item Developed a Flutter app for real-time cryptocurrency price tracking using REST APIs and Provider for state management.
\item Implemented dynamic UI updates, smooth offline support, and error handling.
\item Delivered a responsive, user-friendly experience for crypto enthusiasts.
\end{itemize}

\textbf{Clima App} \hfill {}
\begin{itemize}
\item Created a weather app in Flutter integrating OpenWeatherMap API, geolocation, and manual search.
\item Designed an engaging UI with weather animations and efficient state management.
\item Provided accurate, real-time weather updates with a lightweight, responsive design.
\end{itemize}

\end{rSection}



\begin{rSection}{Education}

{\bf Bachelor of Science in Computer Science}, COMSATS University Islamabad, Attock Campus \hfill {2020 - 2024}

\end{rSection}

 

\begin{rSection}{CERTIFICATIONS} 
\begin{itemize}
    \item The Complete Flutter Development Bootcamp with Dart (Udemy) \href{https://www.udemy.com/certificate/UC-ba57466f-1eaa-48cf-b8c6-621285b2e9c3/}{Certificate}
    \item TensorFlow for Deep Learning Bootcamp (Udemy) \href{https://www.udemy.com/certificate/UC-1cb41d5b-3620-41a2-aa82-33cb4ffe18a7/}{Certificate}
\end{itemize}

\end{rSection}

\end{document}
